---
title: "Keskitalo et al Bayesian source apportionment"
output: github_document
---

This repository contains the code used for fitting a Bayesian model of smoothly varying source proportions in ["Sources and characteristics of terrestrial carbon in Holocene-scale sediments of the East Siberian Sea", *Clim. Past*, 13, 1213-1226, 2017](https://doi.org/10.5194/cp-13-1213-2017)

See `code.R` for R-code and `model.jags` for JAGS model file. Sample run

```{r, warnings = FALSE, message = FALSE, echo = FALSE}
library(ggplot2, quietly = TRUE, warn.conflicts = FALSE)
library(dplyr, quietly = TRUE, warn.conflicts = FALSE)
library(rjags, quietly = TRUE, warn.conflicts = FALSE)
library(splines, quietly = TRUE)
source("code.R")
data<-read.csv("data.csv", sep=";", dec=",", header = FALSE)
colnames(data) <- c("depth", "D14C", "d13C", "year", "sd")
```


```{r, warnings = FALSE, message = FALSE}
mcmc_output <- run_jags(file = "model.jags", data = data, N = 1000000, thin = 1000)
plot_IQR(mcmc_output, data)
```

*Figure: Posterior median and interquartile ranges for source proportions*

```{r}
sessionInfo()
```

